TODO: A Survey of StarCraft AI Techniques

### 2013-02-22 survey.tex
Comment at line 252 in the tex: add chance to hit from low to high ground? which % is right?
CIG competition update 1

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial  reasoning   is  related  to   each  aspect  of   the  terrain
exploitation.  Spatial reasoning is involved in tasks such as building placing, or base expansion. In the former, the player needs to
carefully  consider buildings  position  into its  own  bases to  both
protect them  by creating  a wall against  invasions and to  avoid bad
configurations  where large  units could  be stuck. In base expansion, the player has to
choose good available emplacements to  build a new base, regarding its
own  position  and opponent's  bases.  Finally,  spatial reasoning  is
key to tactical reasoning: players need to decide where to place units for battle, favoring, for  instance, engagements  when the opponent's units are into a  bottleneck. %In Starcraft, it is always an advantage to  have its units  on high ground  whereas enemy is  on low ground, since units  on low ground have no vision  on high ground, and firing from low  ground have only 70\% of chance to  hit units on high ground.

@@

\subsection{CIG 2011}
\label{sec:cig2011}

@@

\begin{table*}[t!]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket A} \\ \hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket B} \\ \hline
Crashes & games & bot	& wins\\ \hline
12 &	 40 &	 Xelnaga &	 25\\
3 &   40 &	 BroodwarBotQ  &  23 (6)\\
0 &	 40 &	 BTHAI	  &  23 (4)\\
17 &	 40 &	 Protoss Beast Jelly  & 17\\
0 &	 40 &	 EvoBot	  &  12\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

\begin{table}[t!]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
Crashes & games & bot	& wins\\ \hline
0 &  30 &	 Skynet	  		&  26\\
0 &	 30 &	 UAlbertaBot 	&  22\\
3 &	 30 &	 Xelnaga  		&  11\\
2 &	 30 &	 BroodwarBotQ  	&  1\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

>>>>

\subsubsection{Spatial and Temporal Reasoning}
% TODO just a paragraph on exposing why there are temporal and spatial
% reasoning in RTS AI.
Spatial  reasoning   is  related  to   each  aspect  of   the  terrain
exploitation.  Spatial reasoning is involved in tasks such as building placing, or base expansion. In the former, the player needs to
carefully  consider buildings  position  into its  own  bases to  both
protect them  by creating  a wall against  invasions and to  avoid bad
configurations  where large  units could  be stuck. In base expansion, the player has to
choose good available emplacements to  build a new base, regarding its
own  position  and opponent's  bases.  Finally,  spatial reasoning  is
key to tactical reasoning: players need to decide where to place units
for battle,  favoring, for  instance, engagements when  the opponent's
units are into a bottleneck.

% [Flo:  70% to hit high  ground units according to  Ben Weber's paper
% [3], and 53.125% according  to BWAPI website. Who's right? Should we
% add this in the paper?]
%In Starcraft, it is always an advantage to  have its units  on high ground  whereas enemy is  on low ground, since units  on low ground have no vision  on high ground, and firing from low  ground have only 70\% of chance to  hit units on high ground.

@@

\subsection{CIG}
\label{sec:cig2011}

@@

\begin{table*}[t!]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:cig-first-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket A} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
A1 & 0 &	 40 &	 UAlbertaBot & 82.5\% \\
A2 & 1 &  	 40 &	 Skynet	  &  77.5\% \\
A3 & 2 &	 40 &	 AIUR	  &  60.0\% \\
A4 & 1 &	 40 &	 Nova	  &  20.0\% \\
A5 & 0 &	 40 &	 LSAI	  &  10.0\%\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|r|}
\hline
\multicolumn{5}{|c|}{Bracket B} \\ \hline
Position & crashes & games & bot	& win\%\\ \hline
B1 & 12 &	 40 &	 Xelnaga &	 62.5\%\\
B2 & 3 &   40 &	 BroodwarBotQ  &  57.5\%\\
B3 & 0 &	 40 &	 BTHAI	  &  57.5\%\\
B4 & 17 &	 40 &	 Protoss Beast Jelly  & 42.5\%\\
B5 & 0 &	 40 &	 EvoBot	  &  30.0\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

@@

\begin{table}[t!]
\caption{Results of the CIG 2011 final round.}
\label{tab:cig-final-round}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|r|}
\hline
Position & crashes & games & bot	& win\%\\ \hline
1 & 0 &  30 &	 Skynet	  		&  86.7\%\\
2 & 0 &	 30 &	 UAlbertaBot 	&  73.3\%\\
3 & 3 &	 30 &	 Xelnaga  		&  36.7\%\\
4 & 2 &	 30 &	 BroodwarBotQ  	&  3.3\%\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table}

For CIG 2012, the AIIDE tournament software was employed,
leading to a total of $4050$ games played in $90$ rounds
of round robin. As 6 different maps were used, this means
that each bot played every other on every map 15 times.
